Constant-round Blind Classical Verification of Quantum Sampling

### 2020-04-16 blind.tex
Sync with local for macro changes

@@

\Ethan{General comment: Make story more interesting. Clearly claim our own contributions.}

We now state our compiler that gives any $\QPIP_0$ protocol blindness.
For notation, when there are many sets of $\QHE$ keys in play at the same time,
we use $\ctx{x}{}{i}$ to denote $x$ encrypted under $pk_i$.
We start with a general form of a $\QPIP_0$ protocol that we'll be compiling.

\begin{protocol}{$\QPIP_0$ protocol $\Pi_0=(P, V)(x)$ where only the verifier receives outputs}

	Common inputs\footnote{For the sake of simplicity, we omit accuracy parameter $\varepsilon$ where it exists}:
	\begin{itemize}
		\item Security parameter $1^\lambda$ where $\lambda\in\bbN$
		\item A classical input $x\in\zo^{\poly(\lambda)}$
	\end{itemize}

@@

We compile the above protocol to achieve blindness as follows.

@@

By the correctness of $\QHE$, the completeness error of $\Piblind$ is negligibly close to that of $\Pi$.
We show the soundness of $\Piblind$ in the following theorem.

\begin{theorem}
	For all cheating $\BQP$ prover $\Pblindstar$, there exists a cheating $\BQP$ prover $\Pstar$ s.t. for all $\lambda$ and input $x\in\zo^{\poly(\lambda)}$, the output distributions of $(\Pblindstar, \Vblind(x))$ and $(\Pstar, V)(x)$ are identical.
\end{theorem}
\begin{proof}
	We define $\Pstar$ as follows.

@@

Finally, we show the blindness of $\Piblind$ through a standard hybrid argument:
\begin{theorem}
	$\Piblind$ is blind.
\end{theorem}
\begin{proof}
	We show that for all cheating $\BQP$ prover $P^*$, $\lambda\in\bbN$, $x\in\zo^n$,
	$P^*$ cannot distinguish $(P^*, \Vblind(x))(1^\lambda)$ from $(P^*, \Vblind(0^n))(1^\lambda)$ with noticeable probability in $\lambda$.
	We use a hybrid argument; let $\Hyb_{T+1}^x=(P^*, \Vblind(x))(1^\lambda)$ and $\Hyb_{T+1}^0=(P^*, \Vblind(0^n))(1^\lambda)$.
	For $2\leq t<T+1$, define $\Hyb_t^x$ to be the same as $\Hyb_{t+1}^x$,
	except when $\Vblind$ should send $\ctx{v}{t}{t}$ and $\ctx{sk}{t-1}{t}$, it instead sends encryptions of $0$ under $pk_t$.
	We define $\Hyb_1^x$ to be the same as $\Hyb_2^x$ except the verifier sends encryptions of $0$ under $pk_1$ in place of $\ctx{x}{}{1}$ and $\ctx{v}{1}{1}$.
	We define $\Hyb_t^0$ similarly. Note that $\Hyb_1^x$ and $\Hyb_1^0$ are identical.

@@

Our compiler is a straightforward way of achievement blindness with existing $\QPIP_0$ protocols while preserving other runtime properties.
In particular, we now apply it to the delegation protocol for $\BQP$ from \cite{parallelrep, alagic2019twomessage},
as well as our $\SampBQP$ protocol $\PiSamp$ to obtain the following results respectively.

@@

\begin{theorem}
	There exists a blind, constant-round $\QPIP_0$ protocol for $\BQP$ with negligible completeness and soundness errors.
\end{theorem}

\begin{theorem}
	There exists a computationally sound, blind, and constant-round $\QPIP_0$ protocol for $\SampBQP$ with negligible completeness errors.
\end{theorem}

>>>>

In this section, we present a generic protocol compiler that compiles any $\QPIP_0$ protocol $\Pi = (P, V)$ (with an arbitrarily number of rounds) to a protocol $\Piblind = (\Pblind, \Vblind)$ that achieve blindness while preserving the completeness, soundness, and round complexity. At a high-level, the idea is simple: we simply run the original protocol under a quantum homomorphic encryption $\QHE$ with the verifier's key. Intuitively, this allows the prover to compute his next message under encryption without learning the underlying verifier's message, and hence achieves blindness while preserving the properties of the original protocol.

However, several issues need to be taking care to make the idea work. First, since the verifier is classical, we need the quantum homomorphic encryption scheme $\QHE$ to be \emph{classical friendly} as defined in Definition~\ref{def:classical-friendly}. Namely, the key generation algorithm and the encryption algorithm for classical messages should be classical, and when the underlying message is classical, the ciphertext (potentially from homomorphic evaluation) and the decryption algorithm should be classical as well. Fortunately, the quantum homomorphic encryption scheme of Mahadev~\cite{mahadev_qfhe} is classical friendly.

A more subtle issue is to preserve the soundness. Intuitively, the soundness holds since the execution of $\Piblind$ simulates the execution of $\Pi$, and hence the soundness of $\Pi$ implies the soundness of $\Piblind$. However, to see the subtle issue, let us consider the following naive compiler that uses a single key: In $\Piblind$,  the verifier $V$ initially generates a pair $\QHE$ key $(pk, sk)$, sends $pk$ and encrypted input $\QEnc(pk,x)$ to $P$. Then they run $\Pi$ under encryption with this key, where both of them use homomorphic evaluation to compute their next message.

There are two reasons that the compiled protocol $\Piblind$ may not be sound (or even not blind). First, in general, the $\QHE$ scheme may not have \emph{circuit privacy}; namely, the homomorphic evaluation may leak information about the circuit being evaluated. Since the verifier computes his next message using homomorphic evaluation, a cheating prover $\Pblindstar$ seeing the homomorphically evaluated ciphertext of the verifier's message may learn information about the verifier's next message circuit, which may contain information about the secret input $x$ or help $\Pblindstar$ to break the soundness. Second, $\Pblindstar$ may send invalid ciphertexts to $V$, so the execution of $\Piblind$ may not simulate a valid execution of $\Pi$.
\Ethan{Either ways, we need $\QHE$ to never fail on decryption, in both this naive $\Piblind$ and our actual $\Piblind$. So there can't be ``invalid ciphertexts" either ways.}

To resolve the issue, we let the verifier to switch to a fresh new key for each round of the protocol. For example, when the prover $\Pblind$ returns the ciphertext of his first message, the verifier $\Vblind$ decrypts the ciphertext \Ethan{Need to mention somewhere that if $\QDec$ fails, it outputs $\bot$ instead of aborting}, computes his next message (in the clear), and then encrypt it using a fresh key $pk'$ and sends it to $\Pblind$. Since the verifier $\Vblind$ only  sends fresh ciphertexts to $\Pblind$, this avoid the issue of circuit privacy. Additionally, to allow $\Pblind$ to homomorphically evaluate its next message, $\Vblind$ needs to encrypt the previous secret key $sk$ under the new public key $pk'$ and send it to $\Pblind$. This allows the prover to homomorphically convert ciphertexts under key $pk$ to ciphertexts under key $pk'$. By doing so, we show that for any cheating prover $\Pblindstar$, the interaction $(\Pblindstar, \Vblind)$ indeed simulates a valid interaction of $(\Pstar, V)$ for some cheating $\Pstar$, and hence the soundness of $\Pi$ implies the soundness of the compiled protocol.

We note that the idea of running the protocol under homomorphic encryptions is used in~\cite{KMThesis} in a classical setting, but for a different purpose of making the protocol ``computationally simulatable'' in their context.

\iffalse

@@

\fi

%\Ethan{General comment: Make story more interesting. Clearly claim our own contributions.}

\KM{notation inconsistency...}

We proceeds to present our compiler. We start by introducing the notation of a $\QPIP_0$ protocol $\Pi$ as follows.
% We now state our compiler that gives any $\QPIP_0$ protocol blindness.

\begin{protocol}{$\QPIP_0$ protocol $\Pi=(P, V)(x)$ where only the verifier receives outputs}

	Common inputs\footnote{For the sake of simplicity, we omit accuracy parameter $\eps$ where it exists}:
	\begin{itemize}
		\item Security parameter $1^\lambda$ where $\lambda\in\bbN$
		\item A classical input $x\in\zo^{\poly(\lambda)}$
	\end{itemize}

@@

We compile the above protocol to achieve blindness as follows.
For notation, when there are many sets of $\QHE$ keys in play at the same time,
we use $\ctx{x}{}{i}$ to denote $x$ encrypted under $pk_i$.
%We start with a general form of a $\QPIP_0$ protocol that we'll be compiling.

@@

By the correctness of $\QHE$, the completeness error of $\Piblind$ is negligibly close to that of $\Pi$.
For the soundness property, we show the following lemma, which implies that $\Piblind$ preserves the soundness of $\Pi_0$.

%soundness of $\Piblind$ in the following theorem.

\begin{thm} \label{thm:compiler-errors}
	For all cheating $\BQP$ prover $\Pblindstar$, there exists a cheating $\BQP$ prover $\Pstar$ s.t. for all $\lambda$ and input $x\in\zo^{\poly(\lambda)}$, the output distributions of $(\Pblindstar, \Vblind(x))$ and $(\Pstar, V)(x)$ are identical.
\end{thm}
\begin{proof}
	We define $\Pstar$ as follows.

@@

Finally, we show the blindness of $\Piblind$ through a standard hybrid argument:
\begin{thm} \label{thm:compiler-blindness}
	Assuming the QLWE assumption, $\Piblind$ is blind.
\end{thm}
\begin{proof}
	We show that for all cheating $\BQP$ prover $P^*$, $\lambda\in\bbN$, $x\in\zo^n$,
	$P^*$ cannot distinguish $(P^*, \Vblind(x))(1^\lambda)$ from $(P^*, \Vblind(0^n))(1^\lambda)$ with noticeable probability in $\lambda$.
	We use a hybrid argument; let $\Hyb_{T+1}^x=(P^*, \Vblind(x))(1^\lambda)$ and $\Hyb_{T+1}^0=(P^*, \Vblind(0^n))(1^\lambda)$.
	For $2\leq t<T+1$, define $\Hyb_t^x$ to be the same as $\Hyb_{t+1}^x$,
	except when $\Vblind$ should send $\ctx{v}{t}{t}$ and $\ctx{sk}{t-1}{t}$, it instead sends encryptions of $0$ under $pk_t$.
	We define $\Hyb_1^x$ to be the same as $\Hyb_2^x$ except the verifier sends encryptions of $0$ under $pk_1$ in place of $\ctx{x}{}{1}$ and $\ctx{v}{1}{1}$.
	We define $\Hyb_t^0$ similarly. Note that $\Hyb_1^x$ and $\Hyb_1^0$ are identical.

@@

Applying our compiler to the parallel repetition of Mahadev's protocol for $\BQP$ from \cite{parallelrep, alagic2019twomessage} and our $\QPIP_0$ protocol $\PiSampZ$ from \Cref{proto:QPIP0samp} for $\SampBQP$ yields the first constant-round blind $\QPIP_0$ protocol for $\BQP$ and $\SampBQP$, respectively.

%Our compiler is a straightforward way of achievement blindness with existing $\QPIP_0$ protocols while preserving other runtime properties.
%In particular, we now apply it to the delegation protocol for $\BQP$ from \cite{parallelrep, alagic2019twomessage},
%as well as our $\SampBQP$ protocol $\PiSamp$ to obtain the following results respectively.

@@

\XW{is this formal enough?}

\begin{cor}
	Assuming the QLWE assumption, there exists a blind, four-message $\QPIP_0$ protocol for all languages in $\BQP$ with negligible completeness and soundness errors.
\end{cor}

\begin{cor}
		Assuming the QLWE assumption, there exists a blind, four-message $\QPIP_0$ protocol for all sampling problems in $\SampBQP$ with negligible completeness error and computational soundness.
		%There exists a computationally sound, blind, and constant-round $\QPIP_0$ protocol for $\SampBQP$ with negligible completeness errors under the QLWE assumption.
\end{cor}

### 2020-04-16 introduction.tex
Sync with local for macro changes

\section{Introduction}
% \XW{ 
% \begin{itemize}
%     \item add a lot of references. 
%     \item comparison with the most relevant results:
%       \begin{itemize}
%           \item Sampling, the only paper; how about classical sampling?
%           \item the following for BQP  
%           \item blind and verifiable ~\cite{GV19}; we  constant round; technique-wise very different. 
%           \item there is a table in~\cite{Grilo19}. Safe to say ~\cite{GV19} only existing blind protocol in the computational setting? 
%           \item all previous either quantum clients, or at least 2 provers. 
%           \item the following for blindess
%           \item Mahadev in her thesis~\cite{mahadev_2018} discussed a bit about the relation between verifiability and blindness. She hoped to get verifiability out of blindness by designing some non-malleable QFHE but failed.   
%           \item what's the high-level message we can say here?  Use QFHE in a different way? It is correct that not much work in the classical setting either.  Maybe existing classical work employs the principle but with different implementation. 
%           \item old approach, first get blindness  (measurement-based, self-testing), and then try to make it verifiable; our approach, first have a verifiable protocol, and upgrade by a QFHE. 
%           \item directly QFHE (blindness) won't give verifiability. some thoughts from Mahadev. 
%           \item 
%       \end{itemize}
% \end{itemize}
% }
Can quantum computation, with potential computational advantages that are intractable for classical computers,
be efficiently verified by classical human being? 
This seemingly paradox has been one of the central problems in quantum complexity theory and delegation of quantum computation~\cite{web:Aaronson}. 
From a philosophical point of view, this question is also known to have a fascinating connection to the \emph{falsifiability} of quantum mechanics in the potential high complexity regime~\cite{survey:AV12}.

A complexity theoretic formulation of this problem by Gottesman in 2004~\cite{web:Aaronson} asks the possibility for an efficient classical verifier/client (a $\BPP$ machine) to verify the output of an
efficient quantum prover (a $\BQP$ machine).
In the absence of techniques for directly tackling this question, earlier feasibility results on this problem have been focusing on two weaker formulations. 
The first type of feasibility results (e.g.,~\cite{BFK09,arXiv:ABOEM17,PR:FitKas17,mf16}) considers the case where the $\BPP$ verifier is equipped with limited quantum power.
The second type of feasibility results (e.g,~\cite{Nat:RUV13, CGJV19, Gheorghiu_2015, HPF15})
considers a $\BPP$ verifier interacting with at least two entangled, non communicating quantum provers. 
In a recent breakthrough, Mahadev~\cite{FOCS:Mahadev18a} proposed the first protocol of classical verification of quantum computation (CVQC) whose soundness is based on a widely recognized computational assumption that the learning with error (LWE) problem~\cite{JACM:Regev09} is hard for $\BQP$ machines. 
The technique invented therein has inspired many  subsequent developments of CVQC protocols with improved parameters and functionality (e.g.~\cite{FOCS:GheVid19,arXiv:AlaChiHun19,arXiv:ChiaChungYam19}). 
We refer curious readers to the survey~\cite{survey:GKK19} for details.

With the newly developed techniques, we revisit the classical verification of quantum computation problem from both a philosophical and a practical point of view. 
We observe that the \emph{sampling} version of $\BQP$ (e.g., the $\SampBQP$ formulated by Aaronson~\cite{aaronson_2013}) might be a more appropriate notion to serve the purpose of the original problem. 
Philosophically, the outcomes of quantum mechanical experiments are usually samples or statistical information, which is well demonstrated in the famous double-slit experiment. 
Moreover, a lot of quantum algorithms from Shor's~\cite{Shor} and Grover's~\cite{Grover} algorithms to some recent developments in machine learning and optimization (e.g.~\cite{brando_et_al:LIPIcs:2019:10603, AGGW17,pmlr-v97-li19b}) contain a significant quantum sampling component. 
The fact that almost all quantum supremacy tasks (e.g.,~\cite{Boson, IQP, nature-google}) are sampling ones strengthens the importance of $\SampBQP$. 
Even though the relation between $\BQP$ and $\SampBQP$ is relatively understood in the plain model, what are the potential technical challenges raised by their subtle differences in the context of CVQC and how to resolve them is however far from clear. 
In particular, it is a prior unclear whether it is feasible to develop a CVQC protocol for $\SampBQP$ based on Mahadev's technique~\cite{FOCS:Mahadev18a}.

@@

\vspace{2mm} \noindent \textbf{Contribution.} We provide \emph{affirmative} solutions to both of our questions. 
In particular, we demonstrate the feasibility of the classical verification of quantum sampling by 
constructing a constant-round CVQC protocol for $\SampBQP$. 
Our protocol leverages the Hamiltonian model and the computational X-Z measurement from~\cite{FOCS:Mahadev18a}.
However, a significant amount of new techniques have been developed to deal with the difference between $\SampBQP$ and $\BQP$, which will be highlighted in the technical contribution below. Precisely,

\XW{Insert the theorem statement for the first result here!}

Blindness Part 
\begin{itemize}
    \item Motivating Blindness
    \item To ADD
    \item Combine both for the results. 
\end{itemize}

Related work
\begin{itemize}
    \item Comparison with related works here?
\end{itemize}

%       \begin{itemize}
%           \item Sampling, the only paper; how about classical sampling?
%           \item the following for BQP  
%           \item blind and verifiable ~\cite{GV19}; we  constant round; technique-wise very different. 
%           \item there is a table in~\cite{Grilo19}. Safe to say ~\cite{GV19} only existing blind protocol in the computational setting? 
%           \item all previous either quantum clients, or at least 2 provers. 
%           \item the following for blindess
%           \item Mahadev in her thesis~\cite{mahadev_2018} discussed a bit about the relation between verifiability and blindness. She hoped to get verifiability out of blindness by designing some non-malleable QFHE but failed.   
%           \item what's the high-level message we can say here?  Use QFHE in a different way? It is correct that not much work in the classical setting either.  Maybe existing classical work employs the principle but with different implementation. 
%           \item old approach, first get blindness  (measurement-based, self-testing), and then try to make it verifiable; our approach, first have a verifiable protocol, and upgrade by a QFHE. 
%           \item directly QFHE (blindness) won't give verifiability. some thoughts from Mahadev. 
%
%           technical comparison with the past parallel % reptiton. 
%           \item

\vspace{2mm} \noindent \textbf{Techniques.}

Technical Contribution
\begin{itemize}
    \item Technical contribution. 
    \item 2nd de finetti have independence; but latter, the analysis, computational parallel repetition. 
    \item TO ADD for both parts. 
\end{itemize}

\vspace{2mm} \noindent \textbf{Open Questions.}
\begin{itemize}
    \item Open questions, and also explain for some associated high-cost. specifically 
    \item T dependence. In general, improve the efficiency.  
    \item negligible soundness error.  compare with classical? what's the state-of-the art. 
\end{itemize}

>>>>

\section{Introduction}
% \XW{ 
% \begin{itemize}
%     \item add a lot of references. 
%     \item comparison with the most relevant results:
%       \begin{itemize}
%           \item Sampling, the only paper; how about classical sampling?
%           \item the following for BQP  
%           \item blind and verifiable ~\cite{GV19}; we  constant round; technique-wise very different. 
%           \item there is a table in~\cite{Grilo19}. Safe to say ~\cite{GV19} only existing blind protocol in the computational setting? 
%           \item all previous either quantum clients, or at least 2 provers. 
%           \item the following for blindess
%           \item Mahadev in her thesis~\cite{mahadev_2018} discussed a bit about the relation between verifiability and blindness. She hoped to get verifiability out of blindness by designing some non-malleable QFHE but failed.   
%           \item what's the high-level message we can say here?  Use QFHE in a different way? It is correct that not much work in the classical setting either.  Maybe existing classical work employs the principle but with different implementation. 
%           \item old approach, first get blindness  (measurement-based, self-testing), and then try to make it verifiable; our approach, first have a verifiable protocol, and upgrade by a QFHE. 
%           \item directly QFHE (blindness) won't give verifiability. some thoughts from Mahadev. 
%           \item 
%       \end{itemize}
% \end{itemize}
% }
Can quantum computation, with potential computational advantages that are intractable for classical computers,
be efficiently verified by classical human being? 
This seeming paradox has been one of the central problems in quantum complexity theory and delegation of quantum computation~\cite{web:Aaronson}. 
From a philosophical point of view, this question is also known to have a fascinating connection to the \emph{falsifiability} of quantum mechanics in the potential high complexity regime~\cite{survey:AV12}.

A complexity theoretic formulation of this problem by Gottesman in 2004~\cite{web:Aaronson} asks the possibility for an efficient classical verifier/client (a $\BPP$ machine) to verify the output of an
efficient quantum prover (a $\BQP$ machine).
In the absence of techniques for directly tackling this question, earlier feasibility results on this problem have been focusing on two weaker formulations. 
The first type of feasibility results (e.g.,~\cite{BFK09,arXiv:ABOEM17,FK17,mf16}) considers the case where the $\BPP$ verifier is equipped with limited quantum power.
The second type of feasibility results (e.g,~\cite{Nat:RUV13, CGJV19, Gheorghiu_2015, HPF15})
considers a $\BPP$ verifier interacting with at least two entangled, non communicating quantum provers. 
In a recent breakthrough, Mahadev~\cite{FOCS:Mahadev18a} proposed the first protocol of classical verification of quantum computation (CVQC) whose soundness is based on a widely recognized computational assumption that the learning with error (LWE) problem~\cite{JACM:Regev09} is hard for $\BQP$ machines. 
The technique invented therein has inspired many  subsequent developments of CVQC protocols with improved parameters and functionality (e.g.~\cite{FOCS:GheVid19,arXiv:AlaChiHun19,arXiv:ChiaChungYam19}). 
We refer curious readers to the survey~\cite{survey:GKK19} for details.

With the newly developed techniques, we revisit the classical verification of quantum computation problem from both a philosophical and a practical point of view. 
We first observe that the \emph{sampling} version of $\BQP$ (e.g., the class $\SampBQP$ formulated by Aaronson~\cite{aaronson_2013}) might be a more appropriate notion to serve the purpose of the original problem. 
Philosophically, the outcomes of quantum mechanical experiments are usually samples or statistical information, which is well demonstrated in the famous double-slit experiment. 
Moreover, a lot of quantum algorithms from Shor's~\cite{Shor} and Grover's~\cite{Grover} algorithms to some recent developments in machine learning and optimization (e.g.~\cite{brando_et_al:LIPIcs:2019:10603, AGGW17,pmlr-v97-li19b}) contain a significant quantum sampling component. 
The fact that almost all quantum supremacy tasks (e.g.,~\cite{Boson, IQP, nature-google}) are sampling ones strengthens the importance of delegation for quantum sampling problems. 
 %Even though the relation between $\BQP$ and $\SampBQP$ is relatively understood in the plain model, 
However, it is far from clear whether the subtle difference between $\BQP$ and its sampling version could lead to 
technical barrier in the context of CVQC, or 
 %what are the potential technical challenges raised by their subtle differences in the context of CVQC and how to resolve them is however far from clear. 
whether one can develop a CVQC protocol for $\SampBQP$ based on Mahadev's technique~\cite{FOCS:Mahadev18a}.

@@

\vspace{2mm} \noindent \textbf{Contribution.} We provide \emph{affirmative} solutions to both of our questions. 
In particular, we demonstrate the feasibility of the classical verification of quantum sampling by 
constructing a constant-round CVQC protocol for $\SampBQP$, the sampling version of $\BQP$ formulated by Aaronson~\cite{aaronson_2013}. Formally, $\SampBQP$ consists of sampling problems $(D_x)_{x\in\zo^*}$ that can be approximately sampled by a $\BQP$ machine with an inverse polynomial accurate. %Namely, $A(x,1^{1/\eps})$ outputs a sample that is $\eps$-close to the distribution $D_x$ in statistical distance.
%, where given an input $x \in \zo^n$, the goal  
Our protocol leverages the Hamiltonian model and the computational X-Z measurement from~\cite{FOCS:Mahadev18a}.
However, a significant amount of new techniques have been developed to deal with the difference between $\SampBQP$ and $\BQP$, which will be highlighted in the technical contribution section. Precisely, 
\begin{theorem}[informal]
Assuming the QLWE assumption, there exists a four-message CVQC protocol for all sampling problems in $\SampBQP$ with negligible completeness error and computational soundness.
\end{theorem}
%\XW{Insert the theorem statement for the first result here! and a pointer!}

Somewhat surprisingly, our second contribution is a simple yet powerful generic compiler that transforms any CVQC protocol to a blind one while preserving completeness and soundness errors.
Our construction builds upon another important primitive called the Quantum Fully Homomorphic Encryption (QFHE)~\cite{BJ15, DSS16, LC18, NS18, OTF18, mahadev_qfhe}.
Intuitively, QFHE allows fully homomorphic operations on encrypted quantum data and thus could be an ideal technical candidate for achieving blindness.
Indeed, in another paper~\cite{mahadev_qfhe}, Mahadev constructed the first leveled QFHE based on similar techniques and computational assumptions from~\cite{FOCS:Mahadev18a}. 
The constructed QFHE automatically implies a blind CVQC protocol, however, without verifiability. 
Extending this protocol with verifiability seems challenging as hinted by failed attempts in~\cite{mahadev_2018}.
In fact, most existing blind and verifiable CVQC protocols requires a notable amount of efforts in achieving each property respectively.

We observe that QFHE, especially the one from~\cite{mahadev_qfhe}, can be used to transform any CVQC protocol to a blind one with the same number of round communication, while preserving completeness and soundness error. 
As a result, one can \emph{upgrade} every verifiable CVQC protocol with blindness almost for free with the help of QFHE. 
Conceptually, we take a very different approach from previous results (e.g.,~\cite{FK17}) which use the blindness as the start point and then work to extend it with verifiability. 
At a high level, our strategy is to simulate the original CVQC protocol under QFHE per each message. 
To that end, we do require a special property of QFHE that the classical part of the ciphertext can be operated on separately from the quantum part, which is satisfied by the construction from~\cite{mahadev_qfhe}.
Our construction makes a modular use of QFHE and only requires a minor technicality in the analysis, which will be explained below. As a result, we obtain
\begin{theorem}[informal]
Assuming the QLWE assumption, there exists a protocol compiler that transforms any CVQC protocol $\Pi$ to a CVQC protocol $\Piblind$ that achieve blindness while preserves its round complexity, completeness, and soundness.
\end{theorem}

\XW{theorem statement for the second contribution and pointer}

As a simple corollary of combining both results above, we achieve a constant-round blind CVQC protocol for $\SampBQP$. %with negligible completeness error and statistical soundness.  
\begin{theorem}[informal]
		Assuming the QLWE assumption, there exists a blind, four-message CVQC protocol for all sampling problems in $\SampBQP$ with negligible completeness error and computational soundness.
\end{theorem}

We can also the first blind and constant-round CVQC protocol for $\BQP$ by applying our compiler to the parallel repetition of Mahadev's protocol for $\BQP$ from \cite{parallelrep, alagic2019twomessage}.

\begin{theorem}[informal]
	Assuming the QLWE assumption, there exists a blind, four-message CVQC protocol for all languages in $\BQP$ with negligible completeness and soundness errors.
\end{theorem}

\XW{here for both $\BQP$ and $\SampBQP$}
\XW{check the para/terminology here; consider adding a theorem statement,or a pointer to the later section}

To the authors' best knowledge, we are the first to study CVQC protocols for $\SampBQP$ and establish a generic compiler to upgrade CVQC protocols with blindness. 
Our result also entails a \emph{constant-round} blind and verifiable CVQC protocol for $\BQP$. 
The closet result to ours is by Gheorghiu and Vidick~\cite{FOCS:GheVid19} which shows such a CVQC protocol for $\BQP$, however, with a polynomial number of rounds. 
Their protocol was obtained by first constructing a remote state preparation primitive and then combining it with an existing blind and verifiable protocol~\cite{FK17} where the verifier has some limited quantum power. 
Our technical approach is quite different and seems incomparable.

% \XW{any more to say about parameters, techniques?}
% \XW{anything we want to say about composability?}
% \Ethan{Last time we checked, Vidick might have better composability since he's got some kind of ideal box and simulator-based proof}

% Related work
% \begin{itemize}
%     \item Comparison with related works here?
% \end{itemize}
%       \begin{itemize}
%           \item Sampling, the only paper; how about classical sampling?
%           \item the following for BQP  
%           \item blind and verifiable ~\cite{GV19}; we  constant round; technique-wise very different. 
%           \item there is a table in~\cite{Grilo19}. Safe to say ~\cite{GV19} only existing blind protocol in the computational setting? 
%           \item all previous either quantum clients, or at least 2 provers. 
%           \item the following for blindess
%           \item Mahadev in her thesis~\cite{mahadev_2018} discussed a bit about the relation between verifiability and blindness. She hoped to get verifiability out of blindness by designing some non-malleable QFHE but failed.   
%           \item what's the high-level message we can say here?  Use QFHE in a different way? It is correct that not much work in the classical setting either.  Maybe existing classical work employs the principle but with different implementation. 
%           \item old approach, first get blindness  (measurement-based, self-testing), and then try to make it verifiable; our approach, first have a verifiable protocol, and upgrade by a QFHE. 
%           \item directly QFHE (blindness) won't give verifiability. some thoughts from Mahadev. 
%
%           technical comparison with the past parallel % reptiton. 
%           \item

\vspace{2mm} \noindent \textbf{Techniques.} Following~\cite{FOCS:Mahadev18a}, we formally define $\QPIP_{\tau}$ as classes of CVQC protocols where $\tau$ refers to the size of quantum register in the possession of the classical verifier, or equivalently, the limited quantum computation power of the verifier. 
It is known that $\BQP$ can be efficiently verified by a classical verifier that can perform a single qubit X or Z measurement~\cite{PhysRevA.93.022326, mf16}. 
Namely, there is a $\QPIP_1$ protocol for $\BQP$. 
The main contribution of Mahadev~\cite{FOCS:Mahadev18a} can hence be deemed as a way to compile this $\QPIP_1$ protocol into a $\QPIP_0$ protocol (i.e., with a fully classical verifier).

\vspace{2mm} \noindent \textbf{(1) Construction of a $\QPIP_0$ protocol for $\SampBQP$}. 
We will follow the same road map above (i.e., from $\QPIP_1$ to $\QPIP_0$) for $\SampBQP$. However, since there is no existing $\QPIP_1$ protocol for $\SampBQP$, we make original contributions to both steps as follows:

\vspace{2mm} \noindent \emph{$\diamond \, \QPIP_1$ protocol for $\SampBQP$}: We will employ the local Hamiltonian technique~\cite{kitaev2002classical} and its ground state (known as the history state) as a key technical ingredient to certify the $\SampBQP$ circuits. 
However, there are important differences between the cases for $\BQP$ and $\SampBQP$. 
Recall that the original construction of local Hamiltonian $H$ for $\BQP$ (or $\QMA$) contains two parts $H=H_{\mathrm{circuit}}+ H_{\mathrm{out}}$. 
Roughly speaking, $H_{\mathrm{circuit}}$ helps guarantee its ground space only contains \emph{valid} history states with correct input and circuit evolution, while $H_{\mathrm{out}}$'s energy encodes the 0/1 output for $\BQP$ circuits. 
Thus, its outcome can be encoded by the \emph{ground energy} of $H$. 
For $\SampBQP$, one still uses $H_{\mathrm{circuit}}$ to certify the validness of the history state. 
However, in this case, one needs to measure on the entire final state of the circuit, rather than a single output qubit, 
which can no longer be encoded solely by the ground energy. 
Our approach is to have the valid history state lie in the ground space of a different local Hamiltonian different $H'_{\mathrm{circuit}}$ that has a large \emph{spectral} gap between its ground energy and excited ones. 
It is hence guaranteed that any state with close-to-ground energy must also be close to the history state. 
In other words, a certification of the energy $H'_{\mathrm{circuit}}$ could lead to a certification of the history state. 
We construct such $H'_{\mathrm{circuit}}$ from $H_{\mathrm{circuit}}$ by using the \emph{perturbation} technique (e.g.,~\cite{kempe_kitaev_regev_2006}) with further restriction to X/Z terms. (\Cref{sec:LHXZ}.)

Another high-level difficulty in constructing a $\QPIP_1$ protocol for $\SampBQP$ is due to the distinction between the test part and the output part. 
Specifically, we will certify the energy of $H'_{\mathrm{circuit}}$ to guarantee the underling state is close to the valid history state. 
However, this procedure could be vastly different from outputting a sample by measuring the final state of $\SampBQP$ circuits. 
We design a \emph{cut-and-choose} protocol on multiple copies of the history state for both testing and outputting. 
We also employ a variant of quantum \emph{de Finetti} theorem~\cite{Brandão2017}
to prevent potential cheating strategies by entangling different copies of history states. 
(\Cref{sec:qpip1}.)

\vspace{2mm} \noindent  \emph{$\diamond$ Compile $\QPIP_1$ into $\QPIP_0$}: 
A naive attempt is to directly apply Mahadev's protocol on the aforementioned $\QPIP_1$ protocol. 
Unfortunately, the plain version of Mahadev's protocol does not yield favorable parameters by itself. 
In fact, there are some recent results~\cite{arXiv:AlaChiHun19, arXiv:ChiaChungYam19} that provide a parallel repetition of Mahadev's original protocol for $\BQP$ with 
much more favorable parameters.

However, we cannot directly make use of these parallel repetition results due to the subtle difference between protocols for $\BQP$ and $\SampBQP$. 
One of the major difficulties here is still to deal with both the test part and the output part in $\SampBQP$ protocols. 
However, because we are now in the computational setting, there is no longer any available quantum de Finetti theorem that is usually derived in the information-theoretic setting. 
We end up of developing a weaker version of parallel repetition result of Mahadev's protocol inspired by the technique from~\cite{arXiv:ChiaChungYam19}. 
Due to the nature of parallel repetition in the computational setting, our analysis is much less modular and significantly involved for this part.  
More intuitions and detailed analysis are given in \Cref{sec:qpip0_all}.

\vspace{2mm} \noindent \textbf{(2) A generic compiler to upgrade $\QPIP_0$ protocols with blindness}. At a high-level, the idea is simple: we run the original protocol under a QFHE with the verifier's key. Intuitively, this allows the prover to compute his next message under encryption without learning the underlying verifier's message, and hence achieves blindness while preserving the properties of the original protocol. 
One subtlety with this approach is due to the fact that the verifer is classical while the QFHE cipher text could depend on both quantum and classical data. 
In order to make the classical verifier work in this construction, the ciphertext and the encryption/decryption algorithm needs to be classical when the underlying message is classical, which is fortunately satisfied by~\cite{mahadev_qfhe}.

A more subtle issue is to preserve the soundness. 
In particular, compiled protocols with only one-time use of QFHE might (1) leak information about the circuit being evaluated during the homomorphic evaluation of QFHE ciphertexts (i.e., no \emph{circuit privacy}); 
or (2) fail to simulate original protocols upon receiving invalid ciphertexts. 
We address these issues by letting the verifier to switch to a fresh new key for each round of the protocol. 
Details are given in \Cref{sec:BlindBQP2}.

\vspace{2mm} \noindent \textbf{Open Questions.}

\begin{itemize}
    \item Open questions, and also explain for some associated high-cost. specifically 
    \item T dependence. In general, improve the efficiency.  
    \item negligible soundness error.  compare with classical? what's the state-of-the art. 
\end{itemize}
